### 2023-09-23 sections/deprecated/training.tex
Update training.tex

\begin{cvhonors}
\cvhonor
{Universidad Católica de Uruguay Winter School in Methods and Data Analysis}
{Training in maths for social sciences, programming in R and Stata, Bayesian statistics, and logit and probit models in R}
{Montevideo, Uruguay}
{2015}
\end{cvhonors}

>>>>

\begin{cvhonors}
\cvhonor
{Universidad Católica de Uruguay Winter School in Methods and Data Analysis}
{Training in maths for social sciences, programming in R and Stata, Bayesian statistics, and logit and probit models in R}
{Montevideo, URY}
{2015}
\end{cvhonors}
